Viscous Erosion in Porous Media

### 2018-02-25 docs/methods/erosion_methods.tex
NM

As a final validation, we now aim to verify the second-order convergence rate (in time) of our method. To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} to a stopping time of $t_s = 1E-2$, which is 56\% of the time it takes for the body to vanish completely. By this time, the body has eroded substantially, but is not so small that accuracy is lost. We assess error by measuring the difference between simulations of successive resolution (i.e.~we verify Cauchy convergence). In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time, $t_s$, while successively doubling the temporal resolution. Table \ref{convtab} shows the $L^2$-errors between successive simulations, along with the order of accuracy as obtained by Richardson-extrapolation-type calculations. The table confirms that our method to converges with second-order accuracy.

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Convergence test: we run erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$ difference in shapes obtained with successive temporal resolution. The tests confirm the method to be second-order accurate in time.
}
\vspace{0.3 pc}
\label{convtab}
\begin{tabular}{c l l}
\hline
\hspace{0.5pc} $\Delta t/t_s$
\hspace{0.5pc} & error 
\hspace{0.5pc} & order \\
\hline
1/100	& 4.69E-6		& --		\\
1/200	& 1.26E-6		& 1.90	\\
1/400	& 3.26E-7		& 1.95	\\
1/800	& 8.28E-8		& 1.98	\\
1/1600	& 2.09E-8		& 1.99	\\
1/3200	& 5.26E-9		& 1.99	\\
1/6400	& --			& --		\\
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Parameters in this test are: 01circ256, nits = 7, dt0 = 1e-4, tfin = 1e-2
% epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 0

>>>>

As a final validation, we now aim to verify the second-order temporal convergence rate of our method. To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} to a stopping time of $t_s = 1E-2$, which is 56\% of the time it takes for the body to vanish completely. By this time, the body has eroded substantially, but is not so small that accuracy is lost. We assess error by measuring the difference between simulations of successive temporal resolution (i.e.~we verify Cauchy convergence). In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time, $t_s$, while successively halving the timestep $\Delta t$. Table \ref{convtab} shows the $L^2$-errors between successive simulations, along with the order of accuracy as obtained by Richardson-extrapolation-type calculations. The table confirms that our method to converges with second-order accuracy.

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Convergence test: we run erosion simulations to a stopping time of $t_s =$ 1E-2 (56\% of the vanishing time) and measure the $L^2$ difference in shapes obtained with successive temporal resolution. The tests confirm the method to be second-order accurate in time.
}
\vspace{0.3 pc}
\label{convtab}
\begin{tabular}{c l l}
\hline
\hspace{0.5pc} $\Delta t/t_s$
\hspace{0.5pc} & error 
\hspace{0.5pc} & order \\
\hline
%
1/50		& 1.68E-5		& --		\\
1/100	& 4.84E-6		& 1.79	\\
1/200	& 1.30E-6		& 1.90	\\
1/400	& 3.36E-7		& 1.95	\\
1/800	& 8.54E-8		& 1.98	\\
1/1600	& 2.15E-8		& 1.99	\\
1/3200	& 5.40E-9		& 1.99	\\
1/6400	& --			& --		\\
%
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Parameters in this test are: 01circ256, nits = 7, dt0 = 1e-4, tfin = 1e-2
% epsfac = 10, sigfac = 10, fixarea = 0, fixprdop = 0

\todo[inline]{Could put CPU time in table too}
